Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-02 GWLDCII.tex

In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace. This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.

@@

The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$. \sanote{Put something about this in the motivation for why WLD $\rightarrow$ GN algorithm is useful}This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.

@@

If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.  So we must have at least one of $m$ and $m+1$ in $I_i$.  However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by the previous paragraph, so permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.  Since $p\in \cP_{in}(p)$ we have $f|\det A${\color{violet}. If we remove the propagators that contribute variables to the minor $C$,}\st{ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$,} we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.  This contradicts the minimality of our choices. \sanote{trying to make clear that the minor changes with the diagram. May have just made it too notation heavy.}

@@

Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.  Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
  \end{enumerate}
\end{proof}
\sanote{start here}

>>>>

In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace. This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$. In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $I(W)$, can be written in terms of the Grassman Necklace of a diagram.

@@

The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$. This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.

@@

If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.  So we must have at least one of $m$ and $m+1$ in $I_i$.  However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark {clockwise ordering rem}}, so permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.  Since $p\in \cP_{in}(p)$ we have $f|\det A${\color{violet}. If we remove the propagators that contribute variables to the minor $C$,}\st{ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$,} we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.  This contradicts the minimality of our choices. \sanote{trying to make clear that the minor changes with the diagram. May have just made it too notation heavy.}

@@

Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.  Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
  \end{enumerate}
\end{proof}
